\chapter*{General Conclusion}
In our project, we have presented some important theoretical and practical principles to keep in mind when designing a data visualization and preventing of Covid-19 propagation, learning common pitfalls and helpful tricks along the way. As we have seen, developing an effective and ethical data visualization is a complex process. \\

We noticed The Benefits of Data Visualization :\\
\textbf{Correlations in Relationships} Without data visualization, it is challenging to identify the correlations between the relationship of independent variables. By making sense of those independent variables, we can make better business decisions. \\

\textbf{Trends Over Time:} While this seems like an obvious use of data visualization, it is also one of the most valuable applications. It’s impossible to make predictions without having the necessary information from the past and present. Trends over time tell us where we were and where we can potentially go.\\

\textbf{Frequency:} Closely related to trends over time is frequency. By examining the rate, or how often, customers purchase and when they buy gives us a better feel for how potential new customers might act and react to different marketing and customer acquisition strategies. 
Examining the Market: Data visualization takes the information from different markets to give you insights into which audiences to focus your attention on and which ones to stay away from. We get a clearer picture of the opportunities within those markets by displaying this data on various charts and graphs.\\

\textbf{Risk and Reward: }Looking at value and risk metrics requires expertise because, without data visualization, we must interpret complicated spreadsheets and numbers. Once information is visualized, we can then pinpoint areas that may or may not require action.\\

\textbf{Reacting to the Market:} The ability to obtain information quickly and easily with data displayed clearly on a functional dashboard allows businesses to act and respond to findings swiftly and helps to avoid making mistakes.\\

For governments and researchers looking to communicate public health information, finding out how simple data visualisations influence the public is now more pressing than ever.
